\section{Wer und warum?}
\subsection{Wer sind wir?}
\begin{frame}{Wer sind wir?}
	\begin{itemize}
		\item blubb 1
		\item blubb 2
	\end{itemize}
\end{frame}

\subsection{Warum crypto?}
\begin{frame}{Why cryptography?}
	\begin{itemize}
		\item Global total surveillance
		\item \emph{selector-based} surveillance
		\item[$\Rightarrow$] Responsibility for people around us as well
		\item Privacy and confidentiality
		\item Keeping (company) secrets
		\item Cryptonoise
	\end{itemize}

	\note[item]{Helping both terrorists and activists to hide.}
	\note[item]{If total observation was fine (and ``no places to hide'' should be left) than this implies that everybody's living room should be subject to surveillance as well.}
	\note[item]{Upside: Less exposure of people around you}
	\note[item]{Downside: Initially one is more interesting --- if you are using crypto something changes on the surveillance radar}
	\note[item]{Last point only valid as long as few people are using crypto}
\end{frame}

\begin{frame}{Why use free software?}
	\begin{block}{Free Software}
		\begin{enumerate}
			\setcounter{enumi}{-1}
			\renewcommand{\theenumi}{\bfseries \arabic{enumi}}
			\item Use the software as you wish
			\item Study the program in source and adapt it as you wish
			\item Redistribute copies to help your neighbour
			\item Distribute modified copies to help the whole community
		\end{enumerate}
	\end{block}

	\begin{block}{Free Software has higher potential to be secure}
		\begin{itemize}
			\item All Software contains bugs
			\item Bugs can be fixed by everyone for everyone
			\item You or person you trust can review source
			\item[$\Rightarrow$] Only free software is really trustworthy
		\end{itemize}
	\end{block}
	\note[item]{Only free operating systems (ie BSD, LinuX) trustworthy}
	\note[item]{Only free hardware trustworthy}
\end{frame}

